\textbf{Causal graph quantum dynamic simulation}

### 2021-06-03 v5/paper/paper.tex
created a new version

\begin{lstlisting}[style=CStyle]
class graph {
	// variables 
	graph_name_t* name_;
	std::vector<unsigned int> left_;
	std::vector<unsigned int> right_;

@@

>>>>

\begin{lstlisting}[style=CStyle]
class graph {
	// split_merge type enum 
  	typedef enum op_type {
		split_t,
		merge_t,
		erase_t,
		create_t,
	} op_type_t;

	// typedef of the pair of an index and a op_type 
  	typedef std::pair<unsigned int, op_type_t> op_t;

	// variables 
	graph_name_t* name_;
	std::vector<unsigned int> left_;
	std::vector<unsigned int> right_;

@@

\subsubsection{erase\_create()}

\begin{lstlisting}[style=CStyle]

void inline graph::erase_create(std::vector<op_t>& erase_create) {
	//...
	void inline erase_create(std::vector<op_t>& erase_create) {
		auto const erase_create_begin = erase_create.rend();

		// add and remove left particules
		auto erase_create_it = erase_create.rbegin();
		int left_idx = left.size() - 1;
		if (!left.empty())
			for (; erase_create_it < erase_create_begin; ++erase_create_it)
				if (erase_create_it->second == create_t) {
					// find the position to insert
					for (; left[left_idx] >= erase_create_it->first && left_idx >= 0; --left_idx) {}

					if (left_idx < 0)
						break;

					// insert
					left.insert(left.begin() + left_idx + 1, erase_create_it->first);

				} else {
					// find the particule to erase 
					for (; left[left_idx] > erase_create_it->first && left_idx >= 0; --left_idx) {}

					if (left_idx < 0)
						break;

					// erase
					left.erase(left.begin() + left_idx);
					--left_idx;
				}

		// add the particule at the begin
		for (; erase_create_it < erase_create_begin; ++erase_create_it)
			left.insert(left.begin(), erase_create_it->first);

		/* add and remove right particules */
	}
	//...
\end{lstlisting}
